The problem and promise of scale in multilayer animal social networks

### 2020-02-15 paper/manuscript.Rmd
small edits

# Abstract
Scale remains a foundational concept in ecology. Spatial scale, for instance,
has become a central consideration in the way we understand landscape ecology
and animal space use. Meanwhile, social processes can also scale from fine-scale
interactions to co-occurrence to overlapping home ranges. <!-- TODO: add
temporal scale --> Multilayer networks promise the integration of monolayer
animal social networks with the complexity and importance of animal space use
and movement in heterogeneous landscapes. Despite the complex interplay between
social networks and how animals use space, there remains an important biological
and methodological gap in our understanding of an animal’s perception of scale.
Here we discuss the role of scale in the context of multilayer networks and
provide a social ungulate case study to illustrate the role of social, spatial,
and temporal scale on multilayer processes. We also present perspectives on
future development and application of scale in multilayer networks with respect
to: habitat selection and space use; phenotypes and individual fitness; and
movement ecology and collective movement. Effective integration of social and
spatial processes, including biologically meaningful scales, within the context
of animal social networks is an emerging area of research, as such our
contribution incorporates perspectives on how the social environment and spatial
processes are linked across scales in a multilayer context.

@@

The integration of behavioural and ecological theory has shown the value of
considering the importance of various ecological disciplines to better
understand and predict animal social networks, including demography
[@Shizuka_2019], evolutionary and quantitative genetics [@Fisher_2017], disease
ecology [@Silk_2017], and animal personality [@Sih_2018]. While the number of
studies integrating social network theory into a broader array of behavioural
and ecological sub-disciplines is impressive, only recently has the role of
animal space use been considered in describing the causes and consequences of
the social environment in the context of (1) phenotypes and individual fitness
[@Webber_2018], (2) movement ecology and collective movement [@Bode_2011], and
(3) habitat selection and space use [@He_2019]. Importantly, much of the work
linking space use and the social environment has been theoretical and empirical
studies are lacking [but see @Peignier_2019;
@Strandburg_Peshkin_2015; @Strandburg_Peshkin_2017]. Here, we discuss the role
mutlilayer networks within the emerging integration of social and spatial
ecology within the behavioural ecology literature.

>>>>

# Abstract
Scale remains a foundational concept in ecology. Spatial scale, for instance,
has become a central consideration in the way we understand landscape ecology
and animal space use. Meanwhile, social processes can also scale from fine-scale
interactions to co-occurrence to overlapping home ranges. <!-- TODO: add
temporal scale --> Multilayer networks promise the integration of monolayer
animal social networks with the complexity and importance of animal space use
and movement in heterogeneous landscapes. Despite the complex interplay between
social networks and how animals use space, there remains an important biological
and methodological gap in our understanding of an animal’s perception of scale.
Here we discuss the role of scale in the context of multilayer networks and
provide a social ungulate case study to illustrate the role of social, spatial,
and temporal scale on multilayer processes. We also present perspectives on
future development and applications of scale in multilayer networks with respect
to: phenotypes and individual fitness, movement ecology and collective movement, and habitat selection and space use. Effective integration of social and
spatial processes, including biologically meaningful scales, within the context
of animal social networks is an emerging area of research, as such our
contribution incorporates perspectives on how the social environment and spatial
processes are linked across scales in a multilayer context.

@@

The integration of behavioural and ecological theory has shown the value of
considering the importance of various ecological disciplines to better
understand and predict animal social networks, including demography
[@Shizuka_2019], evolutionary and quantitative genetics [@Fisher_2017], disease
ecology [@Silk_2017], and animal personality [@Sih_2018]. While the number of
studies integrating social network theory into a broader array of behavioural
and ecological sub-disciplines is impressive, only recently has the role of
animal space use been considered in describing the causes and consequences of
the social environment in the context of (1) phenotypes and individual fitness
[@Webber_2018], (2) movement ecology and collective movement [@Bode_2011], and
(3) habitat selection and space use [@He_2019]. Importantly, much of the work
linking space use and the social environment has been theoretical and empirical
studies are lacking [but see @Peignier_2019; @Strandburg_Peshkin_2015; @Strandburg_Peshkin_2017]. Here, we discuss the role
mutlilayer networks<!-- TODO: withinwithin--> in the emerging integration of
social and spatial ecology within the behavioural ecology literature.
